---
title: Conferences
execute:
  echo: false
df-print: kable
---

```{r setup}
#| message: false
library(tidyverse)
conf_reg <- read_csv("data/conferences-regional.csv")
conf_int <- read_csv("data/conferences-international.csv")
```

## International Biometrics Regional Conference

Our main activity is our regional biennial conference held in odd years. Our last conference was the `r max(year(conf_reg$date_start[conf_reg$date_end < Sys.Date()]))` conference.




```{r}
#| results: asis
conf_reg  |> 
  mutate(name = paste0("[", name, "](", link, ")"),
         year = year(date_start)) |> 
  arrange(desc(year)) |> 
  select(name, date_start, date_end, location) |> 
  pwalk(~{
    cat("### ", ..1, "\n\n")
    cat("{{< fa calendar-alt >}} ", as.character(..2), "--", as.character(..3), "\n\n")
    cat("{{< fa map-pin >}} ", ..4, "\n\n")
  })
```


## International Biometrics Conference

We highly recommend attending the biennial International Biometric Conference (IBC) meetings, which are held in the off-year to our regional meetings, although the planned meeting in Seoul in 2020 was not held. In 2022 it will be held in Riga, Latvia. Conference organisers can use these [Conference Manual & Annexes](https://www.biometricsociety.org/international-biometrics-conference-manual-and-annexes).

See below for further details of previous international conferences.

```{r}
#| results: asis
conf_int  |> 
  mutate(name = ifelse(link!="" & !is.na(link), 
                       paste0("[", name, "](", link, ")"),
                       name),
         year = year(date_start)) |> 
  arrange(desc(year)) |> 
  select(name, date_start, date_end, location) |> 
  pwalk(~{
    cat("### ", ..1, "\n\n")
    cat("{{< fa calendar-alt >}} ", as.character(..2), "--", as.character(..3), "\n\n")
    cat("{{< fa map-pin >}} ", ..4, "\n\n")
  })
```

## Other conferences of interest

If you have a conference of relevance to the biometrical community in Australia or New Zealand, then please contact the contact the Webmaster with details.

