---
title: Conferences
execute:
  echo: false
df-print: kable
---

```{r setup}
#| message: false
library(tidyverse)
conf_reg <- read_csv("data/conferences-regional.csv")
conf_int <- read_csv("data/conferences-international.csv")
```

## International Biometrics Regional Conference

Our main activity is our regional biennial conference held in odd years. Our last conference was the `r max(year(conf_reg$date_start[conf_reg$date_end < Sys.Date()]))` conference.




```{r}
#| results: asis
conf_reg  |> 
  mutate(name = paste0("[", name, "](", link, ")"),
         year = year(date_start),
         md_start = paste0(day(date_start), " ", month(date_start, label = TRUE, abbr = TRUE)),
         md_end = paste0(day(date_end), " ", month(date_end, label = TRUE, abbr = TRUE)),
         date = paste0(md_start, " - ", md_end)) |> 
  arrange(desc(year)) |> 
  select(name, date_start, date_end, location) |> 
  pwalk(~{
    cat("### ", ..1, "\n\n")
    cat("{{< fa calendar-alt >}} ", as.character(..2), "--", as.character(..3), "\n\n")
    cat("{{< fa map-pin >}} ", ..4, "\n\n")
  })
```


## International Biometrics Conference

```{r}
#| results: asis
conf_int  |> 
  arrange(desc(year)) |> 
  select(name, location, year) |> 
  pwalk(~{
    cat("### ", ..1, " ", ..3, "\n\n")
    cat("{{< fa calendar-alt >}} ", as.character(..3), "\n\n")
    cat("{{< fa map-pin >}} ", ..2, "\n\n")
  })
```

## Other conferences of interest

If you have a conference of relevance to the biometrical community in Australia or New Zealand, then please contact the contact the Webmaster with details.

